\chapter{\abstractname}

Institutions and companies are seeking specialized way of learning in digitized education system. 
There are many online education platforms exists today. However,
the gap between the demand and existing education solutions are increasing rapidly.
Specialized set of tracks in online education is needed to address the growing demand.
It is included in many online platforms such as Coursera, Udemy, Udacity and more. 
However, they are in general lack of practical exercises or cheating is relatively easy.
Personalized Cyber security education in practice is generally not available in online education.
There are platforms for practical cyber security education, such as Hackthebox, picoCTF, and more.
However, either they do not provide personalised exercises for the courses at universities, colleges and high schools. 
This platform, named Haaukins, is a specialized virtual platform for cyber security education and exercises are free and specialized for the institutions and companies.
The platform itself is open source and can be found at Github\footnote{https://github.com/aau-network-security/haaukins}.
In this seminar thesis, I will be discussing about how Hauukins platform evolved in time to fulfill the demands of instructors at universities, colleges and high schools.

\makeatletter
\ifthenelse{\pdf@strcmp{\languagename}{english}=1}
{\renewcommand{\abstractname}{Kurzfassung}}
{\renewcommand{\abstractname}{Abstract}}
\makeatother

% \chapter{\abstractname}

% %TODO: Abstract in other language
% \begin{otherlanguage}{ngerman} % TODO: select other language, either ngerman or english !

% \end{otherlanguage}


% % Undo the name switch
% \makeatletter
% \ifthenelse{\pdf@strcmp{\languagename}{english}=0}
% {\renewcommand{\abstractname}{Abstract}}
% {\renewcommand{\abstractname}{Kurzfassung}}
% \makeatother